Recommendation Generation for Performance Improvement by using Cross-Organizational Process Mining

### 2015-09-07 4_methodology/methodology.tex
no message

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved. As proposed in \cite{adriansyah2011conformance, adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models. With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}. For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.

>>>>

\subsubsection{Replay and Performance Indicator Calculation}
\label{subsubsec:replay-and-performance-summary}
Replay of event logs on process models is based on the idea of \textit{alignment} which is formalized in \cite{van2012replaying} and the basic assumption in this concept is that process models and event logs have the same activity labels. Alignment is based on \textit{moves in the model and log} and in order to have a successful replay where optimal alignment should be achieved. As proposed in \cite{adriansyah2011conformance,adriansyah2011towards}, $A^{*}$ algorithm which is a path-finding algorithm based on graphs is used to find optimal alignment of event logs on the process models. With the generated and user-specified inputs, replay and performance indicator calculation in the methodology can be visualized in Figure~\ref{fig:replay-and-performance-indicator-calculation}. For each organization, the steps in the diagram are followed with the corresponding event logs and process models; and the resulting process summaries are used for further analysis.
